### 2021-04-15 paper.Rmd
figure -> Figure

Due to the dynamic nature of the tour, user interfaces can enhance the interpretability of the resulting visualization. Often one will want to pause on a particularly interesting projection and return it for use in a downstream analysis or static plot.  Basic controls can be implemented so a tour display can be paused, refreshed and replayed over and over, as shown in figure \ref{fig:tour-controls}.

@@

Manual tours [@cook_manual_1997; @spyrison_spinifex_2020] offer a means to interactively control the contribution of a single variable on the projection plane. This is particularly useful for exploring a projection once a feature of interest has been identified. Manual tours can then be employed to test the structure of the feature, with respect to a selected variable. For instance, figure \ref{fig:manual-tour}, starts from the orthonormal linear discriminant and explores the sensitivity of class separation as the contribution of a single variable is altered.

>>>>

Due to the dynamic nature of the tour, user interfaces can enhance the interpretability of the resulting visualization. Often one will want to pause on a particularly interesting projection and return it for use in a downstream analysis or static plot.  Basic controls can be implemented so a tour display can be paused, refreshed and replayed over and over, as shown in Figure \ref{fig:tour-controls}.

@@

Manual tours [@cook_manual_1997; @spyrison_spinifex_2020] offer a means to interactively control the contribution of a single variable on the projection plane. This is particularly useful for exploring a projection once a feature of interest has been identified. Manual tours can then be employed to test the structure of the feature, with respect to a selected variable. For instance, Figure \ref{fig:manual-tour}, starts from the orthonormal linear discriminant and explores the sensitivity of class separation as the contribution of a single variable is altered.
